An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.Rmd
Show title

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Melbourne, VIC, Australia
    email: \email{dicook@monash.edu}
title:
  plain: An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With Application to Australian Maps   
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

@@

The hexagon tile map visualisation method can be applied to the Australian Cancer Atlas data. A small example of Lung Cancer Standardised Incidence Rates (SIRs) allows two views of the same data produced by the Australian Cancer Atlas. This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps. The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.

XXX Move this image (ref: sir) to the end of the algorithm section to illustrate the final result for Tassie

@@

The code for sugarbag can be found at XXX, along with details on installation and usage.

>>>>

---
documentclass: jss
author:
  - name: Stephanie Kobakian
    affiliation: Queensland University of Technology
    address: >
      School of Mathematical Sciences,
      Science and Engineering Faculty,
      Brisbane, QLD, Australia
    email: \email{stephanie.kobakian@qut.edu.au}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Melbourne, VIC, Australia
    email: \email{dicook@monash.edu}
title: 
  formatted: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With Application to Australian Maps"
  plain: "An Algorithm For Spatial Mapping Using a Hexagon Tile Map,\nWith Application to Australian Maps"  
abstract: >
  This algorithm creates a tesselated hexagon display to represent each of the spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units. It showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have begun to play a larger role, as alternative representations have been popularised by online news sites, and atlas websites with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results.
keywords:
  # at least one keyword must be supplied
  formatted: [spatial, statistics, cartogram]
preamble: >
  \usepackage{amsmath}
biblio-style: jss
output:
  rticles::jss_article:
    fig_caption: true
    citation_package: natbib
bibliography: sugarbag.bib
link-citations: true
---

@@

A complete hexagon tile map of Tasmania is created by applying the algorithm steps to each centroid.
The hexagon tile map visualisation is used below to visualise the Australian Cancer Atlas data. Two views of the same data are produced by filling according to the Lung Cancer Standardised Incidence Rates (SIRs) downloaded from the Australian Cancer Atlas site. This small example in Figure  \ref{fig:sir} shows the group of blue areas in the Hobart CBD more prominently in the hexagon tile map (b).
The small red areas visible in the choropleth map (a) along the north coast are much larger in the hexagon tile maps. The hexagon tile map shows less yellow, this no longer overwhelms the map space with the information regarding the more rural areas.

@@

```{r liver-geo}
knitr::include_graphics("figures/aus_liver_m.png")
```

```{r liver-hex}
knitr::include_graphics("figures/aus_liver_m_hex.png")
```

@@

The code for sugarbag [@sugarbag] can be found on [CRAN](https://cran.r-project.org/web/packages/sugarbag/index.html), along with vignettes on installation and usage.

### 2020-01-13 kobakian_sugarbag_jss/kobakian_sugarbag_jss.tex
Show title

\author{
Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University
}
\title{}

\Plainauthor{Stephanie Kobakian, Dianne Cook}
\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tilegram, With
Application to Australian Maps}

@@

The hexagon tile map visualisation method can be applied to the
Australian Cancer Atlas data. A small example of Lung Cancer
Standardised Incidence Rates (SIRs) allows two views of the same data
produced by the Australian Cancer Atlas. This small example in Figure
\ref{fig:sir} shows the group of blue areas in the Hobart CBD more
prominently in the hexagon tile map (b). The small red areas visible in
the choropleth map (a) along the north coast are much larger in the
hexagon tile maps. The hexagon tile map shows less yellow, this no
longer overwhelms the map space with the information regarding the more
rural areas.

XXX Move this image (ref: sir) to the end of the algorithm section to
illustrate the final result for Tassie

@@

The code for sugarbag can be found at XXX, along with details on
installation and usage.

>>>>

\author{
Stephanie Kobakian\\Queensland University of Technology \And Dianne Cook\\Monash University
}
\title{An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With
Application to Australian Maps}

\Plainauthor{Stephanie Kobakian, Dianne Cook}
\Plaintitle{An Algorithm For Spatial Mapping Using a Hexagon Tile Map, With
Application to Australian Maps}

@@

\begin{CodeInput}
R> knitr::include_graphics("figures/aus_liver_m.png")
\end{CodeInput}

\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m} \end{center}

\begin{CodeInput}
R> knitr::include_graphics("figures/aus_liver_m_hex.png")
\end{CodeInput}

\begin{center}\includegraphics[width=41.67in]{figures/aus_liver_m_hex} \end{center}

@@

The code for sugarbag \citep{sugarbag} can be found on
\href{https://cran.r-project.org/web/packages/sugarbag/index.html}{CRAN},
along with vignettes on installation and usage.
